Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-10-04 forecast/paper/supplement-text.tex
Update reference

Another relatively assumption-lean method of testing for differences in forecast
accuracy is the Diebold-Mariano test \cite{Diebold:2002,Diebold:2015,harvey1997testing}.
Essentially, the differences between forecast losses are assumed to have a
constant mean and a covariance that depends on time. Under these conditions, the
asymptotic distribution for the standardized mean of the differences is limiting
normal provided that a heteroskedasticity and autocorrelation robust estimate of
the variance is used. Using the loss as weighted interval score across all HRRs
and horizons (7 to 21 days ahead), we perform the DM test using both the mean
relative to the strawman (as reported in the manuscript) and the geometric mean
relative to the strawman as described above. The first two rows of Table
\ref{tab:dm-test} displays 
$P$-values for the test that the indicator-assisted model is no-better than the
AR model. Only the CHNG-CLI model's $P$-value exceeds conventional statistical
significance thresholds.

>>>>

Another relatively assumption-lean method of testing for differences in forecast
accuracy is the Diebold-Mariano test \cite{Diebold:2002, Diebold:2015,
  Harvey:1997}. Essentially, the differences between forecast losses are assumed
to have a constant mean and a covariance that depends on time. Under these
conditions, the asymptotic distribution for the standardized mean of the
differences is limiting normal provided that a heteroskedasticity and
autocorrelation robust estimate of the variance is used. Using the loss as
weighted interval score across all HRRs and horizons (7 to 21 days ahead), we
perform the DM test using both the mean relative to the strawman (as reported in
the manuscript) and the geometric mean relative to the strawman as described
above. The first two rows of Table \ref{tab:dm-test} displays $P$-values for the
test that the indicator-assisted model is no-better than the AR model. Only the
CHNG-CLI model's $P$-value exceeds conventional statistical significance
thresholds.
